Proposal: Loose Grammar Inference for Lossy Compression

### 2012-10-18 proposal.tex
Moar reflow
Starting intro

>>>>

Many sources of data exhibit natural hierarchical structure, but it is
oftentimes difficult to apprehend this structure at a high level due to small
fluctuations in the data at the lower levels of the hierarchy.  If one is
interested primarily in the structure of the data, a lossy compression scheme
has the potential to mitigate some of this low-level noise in favor of the
high-level signal, and can reduce the data size to boot.
